### 2020-09-30 README.Rmd
Some littel changes

run_scbi <- FALSE
run_bw <- TRUE
```

@@

@@

>>>>

run_scbi <- TRUE
run_bw <- TRUE
```

@@

The RMSE is lower for the non-shuffled version. This gives support for the idea that competitor identiy does matter for competitive interactions.

@@

As expected this RMSE is higher than that when the model is fit without cross validation. See Allen and Kim (2020) for more discussion of this.
